Modelling circumstellar discs with 3D radiation hydrodynamics

### 2009-10-12 SPH-Torus-paper1/sphtorus_benchmark.tex
After spell check
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2050 25464f21-6099-402c-b30a-640f1d40d38b

To illustrate the effects of the different splitting methods two
example grids are shown in Fig.~\ref{fig:example_meshes}. A grid
constructed from $10^7$ particles, using a mass per cell limit of
$5\times10^{26}\,\rm{g}$, is plotted in
Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice perpendicular
to the disc mid-plane and shows increased resolution towards the disc
centre and mid-plane where the density is higher.  A grid with
$f_{\rm{split}}=0.1$, also using $10^7$ particles, is plotted in
Fig.~\ref{fig:density_condition_mesh}. The resolution increases
towards the edge of the disc, where there are large density gradients,
and also increases towards the centre of the disc. 
\begin{figure*}
  \subfigure[AMR grid with a mass per cell condition of
    $5\times10^{26}\,\rm{g}$.]
    {\includegraphics[scale=0.22]{figures/set1_mesh}
  \label{fig:mass_condition_mesh}}
  \subfigure[Grid with a density condition of
    $f_{\rm{split}}=0.1$.]
    {\includegraphics[scale=0.22]{figures/set2_mesh}
      \label{fig:density_condition_mesh}}
  \caption{Example AMR grids for a mass per cell splitting condition
    of  $5\times10^{26}\,\rm{g}$ (left)
    and a density contrast splitting condition of $f_{\rm{split}}=0.1$
    (right) contructed
    from $10^7$ SPH particles. The grids are
    slices perpendicular to the disc mid-plane and the axis units are $10^{16}$\,cm.}
  \label{fig:example_meshes}
\end{figure*}

>>>>

To illustrate the effects of the different splitting methods two
example grids are shown in Fig.~\ref{fig:example_meshes}. A grid
constructed from $10^7$ particles, using a mass per cell limit of
$5\times10^{26}\,\rm{g}$, is plotted in
Fig.~\ref{fig:mass_condition_mesh}. This plot is a slice perpendicular
to the disc mid-plane and shows increased resolution towards the disc
centre and mid-plane where the density is higher.  A grid with
$f_{\rm{split}}=0.1$, also using $10^7$ particles, is plotted in
Fig.~\ref{fig:density_condition_mesh}. The resolution increases
towards the edge of the disc, where there are large density gradients,
and also increases towards the centre of the disc. 
\begin{figure*}
  \subfigure[AMR grid with a mass per cell condition of
    $5\times10^{26}\,\rm{g}$.]
    {\includegraphics[scale=0.22]{figures/set1_mesh}
  \label{fig:mass_condition_mesh}}
  \subfigure[Grid with a density condition of
    $f_{\rm{split}}=0.1$.]
    {\includegraphics[scale=0.22]{figures/set2_mesh}
      \label{fig:density_condition_mesh}}
  \caption{Example AMR grids for a mass per cell splitting condition
    of  $5\times10^{26}\,\rm{g}$ (left)
    and a density contrast splitting condition of $f_{\rm{split}}=0.1$
    (right) constructed
    from $10^7$ SPH particles. The grids are
    slices perpendicular to the disc mid-plane and the axis units are $10^{16}$\,cm.}
  \label{fig:example_meshes}
\end{figure*}
